---
title: "Alcohol vs Seat choice"
author: "Claudia Cortez"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
  
```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```   

# Introduction in the year ... 
 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

The data came from UCDavis in the year 

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.   

# Methods  
In the data set davisdata seat is a catagorical variable , alcohol is numerical  

We try and prodict alochol ~ Seat so we use the ... helper file

# Results  

## Desciptive Results    

## Graphical summary  

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

This box plotshows that    
### Numerical summary  






The numerical summery showes that.. 

### Inferential Results 


## Conclusions


