---
title: "Alcohol vs Seat choice"
author: "Claudia Cortez"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
  
```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```   

# Introduction in the year ... 
 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

The data came from UCDavis in the year 1900s.

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.   

# Methods  
In the data set davisdata seat is a catagorical variable , alcohol is numerical  

We try and prodict alochol ~ Seat so we use the ... helper file

# Results  

## Desciptive Results

## Graphical summary  

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

This box plotshows that there are more students who drink alochol seating the back row than the middle and front.    
### Numerical Descriptive Results

```{r}
 favstats(alcohol~Seat,data=ucdavis1)
```

This shows that back seat is consumes 55% more alcohol than the front which is about 20%or middle  which is 35%.


### Inferential Results 
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The p-value is 0.000116, less than 0.05 so we reject the null hypothesis 
There is a difference in alcohol consuption based on wherepeople sit. 


## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```




## Conclusions
The seat in the back has a higher avaerage of people consuming alcohol levels between the diffferent seat position.

